### 2019-04-26 Sections/verification_of_cloud_quantum_computing.tex

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{ZKP_problem_description}	
	\captionspacefig \caption{Problem description for using zero-knowledge proofs as a tool in the commercial outsourcing of quantum problems provided by a classical client (limited to both classial computation and communication) to a quantum-capable server. The proof provided by the server demonstrates that the client's computation has been faithfully executed, without disclosing the outcome before finalising the commercial transaction.}\label{fig:ZKP_problem_description}
\end{figure}

>>>>

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{ZKP_problem_description}	
	\captionspacefig \caption{Problem description for using zero-knowledge proofs as a tool in the commercial outsourcing of quantum problems provided by a classical client (limited to both classical computation and communication) to a quantum-capable server. The proof provided by the server demonstrates that the client's computation has been faithfully executed, without disclosing the outcome before finalising the commercial transaction.}\label{fig:ZKP_problem_description}
\end{figure}
